\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-07-30 jss/article.tex
bibliography fixed

  Hyungsuk Tak\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{tak@fas.harvard.edu}\\

@@

\section[introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.
\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model (R$\ddot{\textrm{o}}$nneg${\aa}$rd et al, 2010), producing point and interval estiates of the true parameters. The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking"). It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).

@@

To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) (another citation) \citep{1997, 2011}. In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family. For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates of the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause. See \cite{2011} for additional advantages of ADM.

>>>>

  Hyungsuk Tak\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{hyungsuk.tak@gmail.com}\\

@@

\section[introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.
\pkg{Rgbp} is an R package for estimating and validating a two-level model, also called conjugate hierarchical generalized linear model \citep{hglm2006, hglm2010}, producing point and interval estiates of the true parameters. The estimation procedure utilizes approximate Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``frequency method checking"). It is found that even in small samples our procedure yields good frequency properties in comparison to other methods such as Maximum Likelihood Estimation (MLE).

@@

To continue with a maximization-based estimation procedure but to steer clear of aforementioned issues we make use of adjustment for density maximization (ADM) \citep{1997, carl1988, 2011}. In general ADM is a procedure to obtain estimates of posterior moments via maximization if the underlying posterior can be approximated by a Pearson family. For our purposes we can approximate the posterior distribution of a shrinkage factor with the Beta distribution allowing us to finally obtain estimates of the posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause. See \cite{2011} for additional advantages of ADM.
